---
title: "NLP exam data cleaning"
author: "Manon Grandjean & Kasper"
date: '2022-11-19'
output: html_document
---

## NLP Exam project 2022 Kasper & Manon
### We have script data from a handfull of sitcoms, but they are not all in the same format
Therefore we need to make sure they all have the same columns and structure

The structure of the column names will be as follows:
Show    Season    Episode   Character   Line    Gender(of character)    IMDB rating(of episode)


```{r Loading packages}
library(tidyverse)
```

### The Big Bang Theory
```{r The Big Bang Theory}
d <- read.csv("1_10_seasons_tbbt.csv")

d$Show <- "The Big Bang Theory"
d <- mutate(.data = d, 
            Season = sub(" Episode.*", "", sub(".*Series ", "", episode_name)),
            Episode = sub(" – Pilot.*","", sub(".*Episode ", "", episode_name)))
d$Character <- d$person_scene
d$Line <- d$dialogue

# there are still some that have episode names (not just numbers)
#MISSING CODE
# gsub("[^0-9.-]", "", x) something something


# make clean dataframe
colnames(d)
data <- d[, c(4,5,6,7,8)]


# remove all rows where the data$Charcter isn't a character or whose gender is not identifiable
# (e.g. Scene, mouths, and photographer)
# see which rows have actual dialog lines in them
unique(data$Character)
data[data$Character == "Scene", ]
data[data$Character == "(mouths)", ]
data[data$Character == "(mouths)", ]

data[str_detect(data$Character, '\\)'), ]
list1 <- data$Character
unique(list1[str_detect(list1, '\\)')])
# There is sometimes real characters that accidentally have an end parenthesis in their name
# "Raj)", "Sheldon)", "Howard)", "Penny(voice)", "Wolowitz)", "Emily)", "Mitch)", "Gablehouser)", "(Wyatt)", "Kevin)", "Leonard)", "Cooper)", "Picard)", "Lucy)", "Penny)", "Priya)", "Ricky)", "Alex)", "Amy(off)", "Penny(leaving)", "Cole)"

# so we need to 'save' these, by removing the parenthesis (and additional irrelevant stuff like '(leaving)')
# data <- str_replace(data$Character, "Raj)", "Raj")
data <- mutate(data, Character = recode(Character, 
                            "Raj)"="Raj",
                            "Sheldon)"="Sheldon",
                            "Howard)"="Howard",
                            "Penny(voice)"="Penny",
                            "Wolowitz)"="Wolowitz",
                            "Emily)"="Emily",
                            "Mitch)"="Mitch",
                            "Gablehouser)"="Gablehouser",
                            "(Wyatt)"="Wyatt",
                            "Kevin)"="Kevin",
                            "Leonard)"="Leonard",
                            "Cooper)"="Cooper",
                            "Picard)"="Picard",
                            "Lucy)"="Lucy",
                            "Penny)"="Penny",
                            "Priya)"="Priya",
                            "Ricky)"="Ricky",
                            "Alex)"="Alex",
                            "Amy(off)"="Amy",
                            "Penny(leaving)"="Penny",
                            "Cole)"="Cole"))



# and then just delete all rows with Character == "Scene" and Character including "\\)"
#data <- data[!str_detect(data$Character, '\\)'), ]






# pick out the top characters, and discarding the rest
uniquenames <- unique(data$Character)
freqlist <- c()

for (uniquename in uniquenames){
  uniquefreq <- length(data[data$Character == uniquename, ]$Character)
  freqlist <- c(freqlist, uniquefreq)
}

namefreqs <- data.frame(uniquenames,freqlist)

# pick out e.g. top 15 speaking characters
top15 <- c("Sheldon","Leonard","Penny","Howard","Raj","Amy","Bernadette","Stuart","Cooper","Priya","Emily","Beverley",
           "Zack","Arthur","Wil")
clean <- data[data$Character %in% top15,]





# label them male (0) or female (1)
clean <- mutate(clean, Gender = recode(Character, 
                                       "Sheldon"=0,
                                       "Leonard"=0,
                                       "Penny"=1,
                                       "Howard"=0,
                                       "Raj"=0,
                                       "Amy"=1,
                                       "Bernadette"=1,
                                       "Stuart"=0,
                                       "Cooper"=0, #is cooper the same character as sheldon?
                                       "Priya"=1,
                                       "Emily"=1,
                                       "Beverley"=1,
                                       "Zack"=0,
                                       "Arthur"=0,
                                       "Wil"=0))

# mean(clean$Gender)
# 30% of lines are spoken by female characters

#Adding gender column
clean$Gender <- as.factor(clean$Gender)

clean <- mutate(clean, Gender_label = recode(Gender, 
                                       "0"="male",
                                       "1"="female"))
clean$Gender <- as.numeric(clean$Gender)


# split into train and test
# we have ~ 14.000 female lines, so if we train on 10.000 female and 10.000 male (sum=20.000) that should be ok
# set.seed(22)
# randomfemale <- subset(clean, Gender == 1)
# randomfemale <- randomfemale[sample(1:nrow(randomfemale)),]
# rf_train <- head(randomfemale, 10000)
# rf_test <- subset(randomfemale, !(Line %in% rf_train$Line)) # doesn't completely take new lines, but I guess it is good
# # that it doesn't see the exact same lines evern when they weren't from the same episode or character...
# randommale <- subset(clean, Gender == 0)
# randommale <- randommale[sample(1:nrow(randommale)),]
# rm_train <- head(randommale, 10000)
# rm_test <- subset(randommale, !(Line %in% rm_train$Line))
# 
# 
# train <- rbind(rf_train, rm_train)
# train <- train[sample(1:nrow(train)),]
# 
# test <- rbind(rf_test, rm_test)
# test <- test[sample(1:nrow(test)),]

clean$Rownumber <- 1:nrow(clean)
clean$Year <- 0

for (i in 1:nrow(clean)){
  if (clean$Rownumber[i] < 1793){
    clean$Year[i] <- "2007"
  }
  else if (clean$Rownumber[i] > 1792 & clean$Rownumber[i] < 5795){
    clean$Year[i] <- "2008"
  }
  else if (clean$Rownumber[i] > 5794 & clean$Rownumber[i] < 10546){
    clean$Year[i] <- "2009"
  }
  else if (clean$Rownumber[i] > 10545 & clean$Rownumber[i] < 15334){
    clean$Year[i] <- "2010"
  }
  else if (clean$Rownumber[i] > 15333 & clean$Rownumber[i] < 20187){
    clean$Year[i] <- "2011"
  }
  else if (clean$Rownumber[i] > 20186 & clean$Rownumber[i] < 24665){
    clean$Year[i] <- "2012"
  }
  else if (clean$Rownumber[i] > 24664 & clean$Rownumber[i] < 29251){
    clean$Year[i] <- "2013"
  }
  else if (clean$Rownumber[i] > 29250 & clean$Rownumber[i] < 34245){
    clean$Year[i] <- "2014"
  }
  else if (clean$Rownumber[i] > 34244 & clean$Rownumber[i] < 39110){
    clean$Year[i] <- "2015"
  }
  else if (clean$Rownumber[i] > 39109 & clean$Rownumber[i] < 44091){
    clean$Year[i] <- "2016"
  }
  else if (clean$Rownumber[i] > 44090){
    clean$Year[i] <- "2017"
  }
} 

# save data
# write.csv(clean, file = "BBTclean.csv")
# write.csv(train, file = "BBTtrain.csv")
# write.csv(test, file = "BBTtest.csv")

write.csv(clean, file = "BBT_Year.csv")
```

The structure of the column names will be as follows:
Show    Season    Episode   Character   Line    Gender(of character)    IMDB rating(of episode)

##Friends
```{r}
#Load in friends data
friends_df <- read_csv("friends_quotes.csv")

friends_df$Show <- "Friends"
names(friends_df)[names(friends_df) == "season"] <- "Season"
names(friends_df)[names(friends_df) == "episode_number"] <- "Episode"
names(friends_df)[names(friends_df) == "author"] <- "Character"
names(friends_df)[names(friends_df) == "quote"] <- "Line"
friends_df$episode_title = NULL
friends_df$quote_order = NULL

uniquenames <- unique(friends_df$Character)
freqlist <- c()

for (uniquename in uniquenames){
  uniquefreq <- length(friends_df[friends_df$Character == uniquename, ]$Character)
  freqlist <- c(freqlist, uniquefreq)
}

namefreqs <- data.frame(uniquenames,freqlist)

friends_df <- mutate(friends_df, Character = recode(Character, 
                            "ROSS"="Ross",
                            "RACHEL"="Rachel",
                            "CHANDLER"="Chandler",
                            "MONICA"="Monica",
                            "PHOEBE"="Phoebe",
                            "JOEY"="Joey",
                            "RACH"="Rachel"))

top15_friends <- c("Ross","Rachel","Chandler","Monica","Phoebe","Joey","Mike","Janice","Charlie",
           "Emily","Mr. Geller","Carol","Tag","David","Paul")
friends_clean <- friends_df[friends_df$Character %in% top15_friends,]

#Adding gender column
friends_clean <- mutate(friends_clean, Gender = recode(Character, 
                                       "Ross"=0,
                                       "Chandler"=0,
                                       "Rachel"=1,
                                       "Joey"=0,
                                       "Mike"=0,
                                       "Monica"=1,
                                       "Phoebe"=1,
                                       "Charlie"=0,
                                       "Mr. Geller"=0, #is cooper the same character as sheldon?
                                       "Carol"=1,
                                       "Emily"=1,
                                       "Janice"=1,
                                       "Paul"=0,
                                       "David"=0,
                                       "Tag"=0))
#checking if all 15 characters are in the df
length(unique(friends_clean$Character))

#Adding gender column
friends_clean$Gender <- as.factor(friends_clean$Gender)

friends_clean <- mutate(friends_clean, Gender_label = recode(Gender, 
                                       "0"="male",
                                       "1"="female"))
friends_clean$Gender <- as.numeric(friends_clean$Gender)

#Adding year
friends_clean$Rownumber <- 1:nrow(friends_clean)
friends_clean$Year <- 0

for (i in 1:nrow(friends_clean)){
  if (friends_clean$Rownumber[i] < 2063){
    friends_clean$Year[i] <- "1994"
  }
  else if (friends_clean$Rownumber[i] > 2062 & friends_clean$Rownumber[i] < 6323){
    friends_clean$Year[i] <- "1995"
  }
  else if (friends_clean$Rownumber[i] > 6322 & friends_clean$Rownumber[i] < 11090){
    friends_clean$Year[i] <- "1996"
  }
  else if (friends_clean$Rownumber[i] > 11089 & friends_clean$Rownumber[i] < 16368){
    friends_clean$Year[i] <- "1997"
  }
  else if (friends_clean$Rownumber[i] > 16367 & friends_clean$Rownumber[i] < 21460){
    friends_clean$Year[i] <- "1998"
  }
  else if (friends_clean$Rownumber[i] > 21459 & friends_clean$Rownumber[i] < 26940){
    friends_clean$Year[i] <- "1999"
  }
  else if (friends_clean$Rownumber[i] > 26939 & friends_clean$Rownumber[i] < 32792){
    friends_clean$Year[i] <- "2000"
  }
  else if (friends_clean$Rownumber[i] > 32791 & friends_clean$Rownumber[i] < 38584){
    friends_clean$Year[i] <- "2001"
  }
  else if (friends_clean$Rownumber[i] > 38583 & friends_clean$Rownumber[i] < 43627){
    friends_clean$Year[i] <- "2002"
  }
  else if (friends_clean$Rownumber[i] > 43626 & friends_clean$Rownumber[i] < 48693){
    friends_clean$Year[i] <- "2003"
  }
  else if (friends_clean$Rownumber[i] > 48692){
    friends_clean$Year[i] <- "2004"
  }
} 

#Writing csv file
write.csv(friends_clean, file = "friends_Year.csv")
```

##Frasier
```{r}
frasier_df <- read_csv("Fraiser_script_no.csv")

#adding and renaming columns
frasier_df$Show <- "Frasier"
names(frasier_df)[names(frasier_df) == "dialog"] <- "Line"
names(frasier_df)[names(frasier_df) == "cast"] <- "Character"

uniquenames <- unique(frasier_df$Character)
freqlist <- c()

for (uniquename in uniquenames){
  uniquefreq <- length(frasier_df[frasier_df$Character == uniquename, ]$Character)
  freqlist <- c(freqlist, uniquefreq)
}

namefreqs <- data.frame(uniquenames,freqlist)

top15_frasier <- c("Frasier","Niles","Martin","Daphne","Roz","Bulldog","Lilith","Kenny","Bebe",
           "Donny","Freddie","Charlotte","Ronee","Sherry","Gil")
frasier_clean <- frasier_df[frasier_df$Character %in% top15_frasier,]

#Adding gender column
frasier_clean <- mutate(frasier_clean, Gender = recode(Character, 
                                       "Frasier"=0,
                                       "Niles"=0,
                                       "Daphne"=1,
                                       "Martin"=0,
                                       "Roz"=1,
                                       "Bulldog"=0,
                                       "Lilith"=1,
                                       "Kenny"=0,
                                       "Bebe"=1, #is cooper the same character as sheldon?
                                       "Donny"=0,
                                       "Freddie"=0,
                                       "Charlotte"=1,
                                       "Ronee"=1,
                                       "Sherry"=0,
                                       "Gil"=0))

#Adding gender label
frasier_clean$Gender <- as.factor(frasier_clean$Gender)

frasier_clean <- mutate(frasier_clean, Gender_label = recode(Gender, 
                                       "0"="male",
                                       "1"="female"))
frasier_clean$Gender <- as.numeric(frasier_clean$Gender)
#checking if all 15 characters are in the df
length(unique(frasier_clean$Character))

#Adding year
frasier_clean$Rownumber <- 1:nrow(frasier_clean)
frasier_clean$Year <- 0

for (i in 1:nrow(frasier_clean)){
  if (frasier_clean$Rownumber[i] < 2344){
    frasier_clean$Year[i] <- "1993"
  }
  else if (frasier_clean$Rownumber[i] > 2343 & frasier_clean$Rownumber[i] < 6732){
    frasier_clean$Year[i] <- "1994"
  }
  else if (frasier_clean$Rownumber[i] > 6731 & frasier_clean$Rownumber[i] < 11076){
    frasier_clean$Year[i] <- "1995"
  }
  else if (frasier_clean$Rownumber[i] > 11075 & frasier_clean$Rownumber[i] < 15398){
    frasier_clean$Year[i] <- "1996"
  }
  else if (frasier_clean$Rownumber[i] > 15397 & frasier_clean$Rownumber[i] < 20749){
    frasier_clean$Year[i] <- "1997"
  }
  else if (frasier_clean$Rownumber[i] > 20748 & frasier_clean$Rownumber[i] < 26149){
    frasier_clean$Year[i] <- "1998"
  }
  else if (frasier_clean$Rownumber[i] > 26148 & frasier_clean$Rownumber[i] < 31770){
    frasier_clean$Year[i] <- "1999"
  }
  else if (frasier_clean$Rownumber[i] > 31769 & frasier_clean$Rownumber[i] < 36147){
    frasier_clean$Year[i] <- "2000"
  }
  else if (frasier_clean$Rownumber[i] > 36146 & frasier_clean$Rownumber[i] < 41594){
    frasier_clean$Year[i] <- "2001"
  }
  else if (frasier_clean$Rownumber[i] > 41593 & frasier_clean$Rownumber[i] < 45366){
    frasier_clean$Year[i] <- "2002"
  }
  else if (frasier_clean$Rownumber[i] > 45365 & frasier_clean$Rownumber[i] < 49815){
    frasier_clean$Year[i] <- "2003"
  }
  else if (frasier_clean$Rownumber[i] > 49814){
    frasier_clean$Year[i] <- "2004"
  }
}

#Writing csv file
write.csv(frasier_clean, file = "frasier_Year.csv")
```
## Parks and rec

```{r}
PaR_df <- read_csv("parks_and_rec_scripts.csv")
PaR_df$...1 <- NULL
PaR_df$Show <- "Parks and recreation"

uniquenames <- unique(PaR_df$Character)
freqlist <- c()

for (uniquename in uniquenames){
  uniquefreq <- length(PaR_df[PaR_df$Character == uniquename, ]$Character)
  freqlist <- c(freqlist, uniquefreq)
}

namefreqs <- data.frame(uniquenames,freqlist)

top15_PaR <- c("Leslie Knope","Tom Haverford","Andy Dwyer","Ben Wyatt","Ron Swanson","Ann Perkins","April Ludgate","Chris Traeger","Donna Meagle",
           "Jerry Gergich","Mark Brendanawicz","Jeremy Jamm","Jean-Ralphio Saperstein","Jennifer Barkley","Dave Sanderson")
PaR_clean <- PaR_df[PaR_df$Character %in% top15_PaR,]

#Adding gender column
PaR_clean <- mutate(PaR_clean, Gender = recode(Character, 
                                       "Leslie Knope"=1,
                                       "Tom Haverford"=0,
                                       "Andy Dwyer"=0,
                                       "Ben Wyatt"=0,
                                       "Ron Swanson"=0,
                                       "Ann Perkins"=1,
                                       "April Ludgate"=1,
                                       "Chris Traeger"=0,
                                       "Donna Meagle"=1, #is cooper the same character as sheldon?
                                       "Jerry Gergich"=0,
                                       "Mark Brendanawicz"=0,
                                       "Jeremy Jamm"=0,
                                       "Jean-Ralphio Saperstein"=0,
                                       "Jennifer Barkley"=1,
                                       "Dave Sanderson"=0))

#Adding gender label
PaR_clean$Gender <- as.factor(PaR_clean$Gender)

PaR_clean <- mutate(PaR_clean, Gender_label = recode(Gender, 
                                       "0"="male",
                                       "1"="female"))
PaR_clean$Gender <- as.numeric(PaR_clean$Gender)

#checking if all 15 characters are in the df
length(unique(PaR_clean$Character))

#Adding year
PaR_clean$Rownumber <- 1:nrow(PaR_clean)
PaR_clean$Year <- 0

for (i in 1:nrow(PaR_clean)){
  if (PaR_clean$Rownumber[i] < 8216){
    PaR_clean$Year[i] <- "2009"
  }
  else if (PaR_clean$Rownumber[i] > 8215 & PaR_clean$Rownumber[i] < 14165){
    PaR_clean$Year[i] <- "2010"
  }
  else if (PaR_clean$Rownumber[i] > 14164 & PaR_clean$Rownumber[i] < 26489){
    PaR_clean$Year[i] <- "2011"
  }
  else if (PaR_clean$Rownumber[i] > 26488 & PaR_clean$Rownumber[i] < 35901){
    PaR_clean$Year[i] <- "2012"
  }
  else if (PaR_clean$Rownumber[i] > 35900 & PaR_clean$Rownumber[i] < 45661){
    PaR_clean$Year[i] <- "2013"
  }
  else if (PaR_clean$Rownumber[i] > 45660 & PaR_clean$Rownumber[i] < 50658){
    PaR_clean$Year[i] <- "2014"
  }
  else if (PaR_clean$Rownumber[i] > 50657){
    PaR_clean$Year[i] <- "2015"
  }
} 

write.csv(PaR_clean, file = "Parks_and_rec_Year.csv")
```
##Seinfeld

```{r}
seinfeld_df <- read_csv("Seinfeld-scripts-Kaggle-LSM_DAT_SCI.csv")

seinfeld_df$Show <- "Seinfeld"
names(seinfeld_df)[names(seinfeld_df) == "season"] <- "Season"
names(seinfeld_df)[names(seinfeld_df) == "episode"] <- "Episode"
names(seinfeld_df)[names(seinfeld_df) == "character"] <- "Character"
names(seinfeld_df)[names(seinfeld_df) == "dialogue"] <- "Line"

uniquenames <- unique(seinfeld_df$Character)
freqlist <- c()

for (uniquename in uniquenames){
  uniquefreq <- length(seinfeld_df[seinfeld_df$Character == uniquename, ]$Character)
  freqlist <- c(freqlist, uniquefreq)
}

namefreqs <- data.frame(uniquenames,freqlist)

top15_seinfeld <- c("JERRY","GEORGE","ELAINE","KRAMER","NEWMAN","MORTY","HELEN","FRANK","SUSAN",
           "ESTELLE","PUDDY","PETERMAN","LEO","JACK","LIPPMAN")
seinfeld_clean <- seinfeld_df[seinfeld_df$Character %in% top15_seinfeld,]

#Adding gender column
seinfeld_clean <- mutate(seinfeld_clean, Gender = recode(Character, 
                                       "JERRY"=0,
                                       "GEORGE"=0,
                                       "ELAINE"=1,
                                       "KRAMER"=0,
                                       "NEWMAN"=0,
                                       "MORTY"=0,
                                       "HELEN"=1,
                                       "FRANK"=0,
                                       "SUSAN"=1, #is cooper the same character as sheldon?
                                       "ESTELLE"=1,
                                       "PUDDY"=0,
                                       "PETERMAN"=0,
                                       "LEO"=0,
                                       "JACK"=0,
                                       "LIPPMAN"=0))

#Adding gender label
seinfeld_clean$Gender <- as.factor(seinfeld_clean$Gender)

seinfeld_clean <- mutate(seinfeld_clean, Gender_label = recode(Gender, 
                                       "0"="male",
                                       "1"="female"))
seinfeld_clean$Gender <- as.numeric(seinfeld_clean$Gender)

#checking if all 15 characters are in the df
length(unique(seinfeld_clean$Character))

#Adding year
seinfeld_clean$Rownumber <- 1:nrow(seinfeld_clean)
seinfeld_clean$Year <- 0

for (i in 1:nrow(seinfeld_clean)){
  if (seinfeld_clean$Rownumber[i] < 188){
    seinfeld_clean$Year[i] <- "1989"
  }
  else if (seinfeld_clean$Rownumber[i] > 187 & seinfeld_clean$Rownumber[i] < 1152){
    seinfeld_clean$Year[i] <- "1990"
  }
  else if (seinfeld_clean$Rownumber[i] > 1151 & seinfeld_clean$Rownumber[i] < 6787){
    seinfeld_clean$Year[i] <- "1991"
  }
  else if (seinfeld_clean$Rownumber[i] > 6786 & seinfeld_clean$Rownumber[i] < 12787){
    seinfeld_clean$Year[i] <- "1992"
  }
  else if (seinfeld_clean$Rownumber[i] > 12786 & seinfeld_clean$Rownumber[i] < 17934){
    seinfeld_clean$Year[i] <- "1993"
  }
  else if (seinfeld_clean$Rownumber[i] > 17933 & seinfeld_clean$Rownumber[i] < 23141){
    seinfeld_clean$Year[i] <- "1994"
  }
  else if (seinfeld_clean$Rownumber[i] > 23140 & seinfeld_clean$Rownumber[i] < 28839){
    seinfeld_clean$Year[i] <- "1995"
  }
  else if (seinfeld_clean$Rownumber[i] > 28838 & seinfeld_clean$Rownumber[i] < 34800){
    seinfeld_clean$Year[i] <- "1996"
  }
  else if (seinfeld_clean$Rownumber[i] > 34799 & seinfeld_clean$Rownumber[i] < 40404){
    seinfeld_clean$Year[i] <- "1997"
  }
  else if (seinfeld_clean$Rownumber[i] > 40403){
    seinfeld_clean$Year[i] <- "1998"
  }
}

write.csv(seinfeld_clean, file = "seinfeld_Year.csv")
```

##The office

```{r}
TO_df <- read_csv("The-Office-Lines-V4 2 (1).csv")

TO_df$Show <- "The Office"
names(TO_df)[names(TO_df) == "season"] <- "Season"
names(TO_df)[names(TO_df) == "episode"] <- "Episode"
names(TO_df)[names(TO_df) == "speaker"] <- "Character"
names(TO_df)[names(TO_df) == "line"] <- "Line"
TO_df$...7 <- NULL
TO_df$scene <- NULL
TO_df$title <- NULL

uniquenames <- unique(TO_df$Character)
freqlist <- c()

for (uniquename in uniquenames){
  uniquefreq <- length(TO_df[TO_df$Character == uniquename, ]$Character)
  freqlist <- c(freqlist, uniquefreq)
}

namefreqs <- data.frame(uniquenames,freqlist)


top15_TO <- c("Michael","Jim","Dwight","Pam","Andy","Kevin","Angela","Erin","Oscar",
           "Ryan","Darryl","Phyllis","Kelly","Toby","Jan")
TO_clean <- TO_df[TO_df$Character %in% top15_TO,]

#Adding gender column
TO_clean <- mutate(TO_clean, Gender = recode(Character, 
                                       "Michael"=0,
                                       "Jim"=0,
                                       "Pam"=1,
                                       "Dwight"=0,
                                       "Andy"=0,
                                       "Kevin"=0,
                                       "Angela"=1,
                                       "Oscar"=0,
                                       "Erin"=1, #is cooper the same character as sheldon?
                                       "Phyllis"=1,
                                       "Darryl"=0,
                                       "Toby"=0,
                                       "Ryan"=0,
                                       "Jan"=1,
                                       "Kelly"=1))

#Adding gender label
TO_clean$Gender <- as.factor(TO_clean$Gender)

TO_clean <- mutate(TO_clean, Gender_label = recode(Gender, 
                                       "0"="male",
                                       "1"="female"))
TO_clean$Gender <- as.numeric(TO_clean$Gender)

#checking if all 15 characters are in the df
length(unique(TO_clean$Character))

#Adding year
TO_clean$Rownumber <- 1:nrow(TO_clean)
TO_clean$Year <- 0

for (i in 1:nrow(TO_clean)){
  if (TO_clean$Rownumber[i] < 3728){
    TO_clean$Year[i] <- "2005"
  }
  else if (TO_clean$Rownumber[i] > 3727 & TO_clean$Rownumber[i] < 8753){
    TO_clean$Year[i] <- "2006"
  }
  else if (TO_clean$Rownumber[i] > 8752 & TO_clean$Rownumber[i] < 14253){
    TO_clean$Year[i] <- "2007"
  }
  else if (TO_clean$Rownumber[i] > 14252 & TO_clean$Rownumber[i] < 18380){
    TO_clean$Year[i] <- "2008"
  }
  else if (TO_clean$Rownumber[i] > 18379 & TO_clean$Rownumber[i] < 25497){
    TO_clean$Year[i] <- "2009"
  }
  else if (TO_clean$Rownumber[i] > 25496 & TO_clean$Rownumber[i] < 31028){
    TO_clean$Year[i] <- "2010"
  }
  else if (TO_clean$Rownumber[i] > 31027 & TO_clean$Rownumber[i] < 36014){
    TO_clean$Year[i] <- "2011"
  }
  else if (TO_clean$Rownumber[i] > 36013 & TO_clean$Rownumber[i] < 40780){
    TO_clean$Year[i] <- "2012"
  }
  else if (TO_clean$Rownumber[i] > 40779){
    TO_clean$Year[i] <- "2013"
  }
}

write.csv(TO_clean, file = "The_Office_Year.csv")
```

##How I met your mother
```{r}
HIMYM_df_new <- read_csv("HIMYM_data.csv")

HIMYM_df_new$Show <- "How I met your mother"
names(HIMYM_df_new)[names(HIMYM_df_new) == "season"] <- "Season"
names(HIMYM_df_new)[names(HIMYM_df_new) == "episode"] <- "Episode"
names(HIMYM_df_new)[names(HIMYM_df_new) == "actor"] <- "Character"
names(HIMYM_df_new)[names(HIMYM_df_new) == "text"] <- "Line"
HIMYM_df_new$title <- NULL

uniquenames <- unique(HIMYM_df_new$Character)
freqlist <- c()

for (uniquename in uniquenames){
  uniquefreq <- length(HIMYM_df_new[HIMYM_df_new$Character == uniquename, ]$Character)
  freqlist <- c(freqlist, uniquefreq)
}

namefreqs <- data.frame(uniquenames,freqlist)

top15_HIMYM <- c("Ted","Barney","Marshall","Robin","Lily","Stella","Zoey","Victoria","Nora",
           "Jerry","Mr Druthers","Don","James","Arthur","Ranjit")
HIMYM_clean <- HIMYM_df_new[HIMYM_df_new$Character %in% top15_HIMYM,]

#Adding gender column
HIMYM_clean <- mutate(HIMYM_clean, Gender = recode(Character, 
                                       "Ted"=0,
                                       "Barney"=0,
                                       "Robin"=1,
                                       "Marshall"=0,
                                       "Lily"=1,
                                       "Stella"=1,
                                       "Zoey"=1,
                                       "Victoria"=1,
                                       "Nora"=1, #is cooper the same character as sheldon?
                                       "Jerry"=0,
                                       "Mr Druthers"=0,
                                       "Don"=0,
                                       "James"=0,
                                       "Arthur"=0,
                                       "Ranjit"=0))

#Adding gender label
HIMYM_clean$Gender <- as.factor(HIMYM_clean$Gender)

HIMYM_clean <- mutate(HIMYM_clean, Gender_label = recode(Gender, 
                                       "0"="male",
                                       "1"="female"))
HIMYM_clean$Gender <- as.numeric(HIMYM_clean$Gender)

#checking if all 15 characters are in the df
length(unique(HIMYM_clean$Character))

#Adding year
HIMYM_clean$Rownumber <- 1:nrow(HIMYM_clean)
HIMYM_clean$Year <- 0

for (i in 1:nrow(HIMYM_clean)){
  if (HIMYM_clean$Rownumber[i] < 2332){
    HIMYM_clean$Year[i] <- "2005"
  }
  else if (HIMYM_clean$Rownumber[i] > 2331 & HIMYM_clean$Rownumber[i] < 6791){
    HIMYM_clean$Year[i] <- "2006"
  }
  else if (HIMYM_clean$Rownumber[i] > 6790 & HIMYM_clean$Rownumber[i] < 10202){
    HIMYM_clean$Year[i] <- "2007"
  }
  else if (HIMYM_clean$Rownumber[i] > 10201 & HIMYM_clean$Rownumber[i] < 13511){
    HIMYM_clean$Year[i] <- "2008"
  }
  else if (HIMYM_clean$Rownumber[i] > 13510 & HIMYM_clean$Rownumber[i] < 17808){
    HIMYM_clean$Year[i] <- "2009"
  }
  else if (HIMYM_clean$Rownumber[i] > 17807 & HIMYM_clean$Rownumber[i] < 22118){
    HIMYM_clean$Year[i] <- "2010"
  }
  else if (HIMYM_clean$Rownumber[i] > 22117 & HIMYM_clean$Rownumber[i] < 24731){
    HIMYM_clean$Year[i] <- "2011"
  }
  else if (HIMYM_clean$Rownumber[i] > 24730 & HIMYM_clean$Rownumber[i] < 24869){
    HIMYM_clean$Year[i] <- "2012"
  }
  else if (HIMYM_clean$Rownumber[i] > 24868){
    HIMYM_clean$Year[i] <- "2013"
  }
} 

write.csv(HIMYM_clean, file = "How_I_met_your_mother_Year.csv")
```

```{r}
str(clean)
for (i in 1:4){
  split <- str_split(clean$Line[i], " ")
  print(length(split)[1])
}

print(clean$Line[1])
splittest <- str_split(clean$Line[1], " ")
print(splittest)

combined$N_words <- sapply(strsplit(combined$Line, " "),length)
combined$N_words <- combined$N_words-1
subset_combined <- subset(combined, N_words > 3)
```


```{r}
#Combine all the datasets
combined <- rbind(clean, friends_clean, PaR_clean, HIMYM_clean, TO_clean, seinfeld_clean, frasier_clean)

plot(frequency(combined$Gender), combined$Year)
```

```{r}
subset_combined$Year_groups <- 0

str(subset_combined)

group1 <- subset(subset_combined, Year == "1989")
group1$Year_groups <- "1989-1993"
group2 <- subset(subset_combined, Year == "1990")
group2$Year_groups <- "1989-1993"
group3 <- subset(subset_combined, Year == "1991")
group3$Year_groups <- "1989-1993"
group4 <- subset(subset_combined, Year == "1992")
group4$Year_groups <- "1989-1993"
group5 <- subset(subset_combined, Year == "1993")
group5$Year_groups <- "1989-1993"
group6 <- subset(subset_combined, Year == "1994")
group6$Year_groups <- "1994-1997"
group7 <- subset(subset_combined, Year == "1995")
group7$Year_groups <- "1994-1997"
group8 <- subset(subset_combined, Year == "1996")
group8$Year_groups <- "1994-1997"
group9 <- subset(subset_combined, Year == "1997")
group9$Year_groups <- "1994-1997"
group10 <- subset(subset_combined, Year == "1998")
group10$Year_groups <- "1998-2001"
group11 <- subset(subset_combined, Year == "1999")
group11$Year_groups <- "1998-2001"
group12 <- subset(subset_combined, Year == "2000")
group12$Year_groups <- "1998-2001"
group13 <- subset(subset_combined, Year == "2001")
group13$Year_groups <- "1998-2001"
group14 <- subset(subset_combined, Year == "2002")
group14$Year_groups <- "2002-2005"
group15 <- subset(subset_combined, Year == "2003")
group15$Year_groups <- "2002-2005"
group16 <- subset(subset_combined, Year == "2004")
group16$Year_groups <- "2002-2005"
group17 <- subset(subset_combined, Year == "2005")
group17$Year_groups <- "2002-2005"
group18 <- subset(subset_combined, Year == "2006")
group18$Year_groups <- "2006-2009"
group19 <- subset(subset_combined, Year == "2007")
group19$Year_groups <- "2006-2009"
group20 <- subset(subset_combined, Year == "2008")
group20$Year_groups <- "2006-2009"
group21 <- subset(subset_combined, Year == "2009")
group21$Year_groups <- "2006-2009"
group22 <- subset(subset_combined, Year == "2010")
group22$Year_groups <- "2010-2013"
group23 <- subset(subset_combined, Year == "2011")
group23$Year_groups <- "2010-2013"
group24 <- subset(subset_combined, Year == "2012")
group24$Year_groups <- "2010-2013"
group25 <- subset(subset_combined, Year == "2013")
group25$Year_groups <- "2010-2013"
group26 <- subset(subset_combined, Year == "2014")
group26$Year_groups <- "2014-2017"
group27 <- subset(subset_combined, Year == "2015")
group27$Year_groups <- "2014-2017"
group28 <- subset(subset_combined, Year == "2016")
group28$Year_groups <- "2014-2017"
group29 <- subset(subset_combined, Year == "2017")
group29$Year_groups <- "2014-2017"

groupyear_combined <- rbind(group1, group2, group3, group4, group5, group6, group7, group8, group9, group10, group11, group12, group13, group14, group15, group16, group17, group18, group19, group20, group21, group22, group23, group24, group25, group26, group27, group28, group29)

hist(groupyear_combined$Year_groups=="1989-1993")

write.csv(groupyear_combined, file = "With_yeargroups.csv")
```

```{r}
groupedby <- groupyear_combined %>% group_by(Gender_label) %>% summarise(number_of_lines = n())

male_group <- subset(groupyear_combined, Gender_label == "male")
female_group <- subset(groupyear_combined, Gender_label == "female")
female_group1 <- female_group
new_female_group <- rbind(female_group, female_group1)

write.csv(male_group, file = "male_group.csv")
write.csv(female_group, file = "female_group.csv")
```


```{r}
testtestdf <- groupyear_combined
testtestdf$Line <- gsub("\\b[^[:alnum:],.?!'’]+\\b", " ", testtestdf$Line)
write.csv(groupyear_combined, file = "characters_filtered.csv")
str(testtestdf)
testmand <- subset(testtestdf, Season == 10)
write.csv(testmand, file = "test_for_sentiment.csv")
```

```{r}
library(tidyverse)
output <- read.csv("output.csv")
output_neutral <- read_csv("output_sentiment_neurtral.csv")

neutral_removed <- subset(output_neutral, sentiment != "neutral" )

write.csv(neutral_removed, file = "neutral_removed.csv")
```

```{r}
emotion_df <- read_csv("emotion_df.csv")
groupedby_ES <- emotion_df %>% group_by(Year_groups, Gender_label) %>% summarise(number_of_lines = n())
```

```{r}
install.packages("lmerTest")
library(lmerTest)
str(emotion_df)
lm <- lmer(Gender~Emotion_sentiment+(1|Show),data=emotion_df)
summary(lm)

lm1 <- lm(Gender ~ 0 + Emotion_sentiment,data=emotion_df)
summary(lm1)

lm2 <- lm(Gender~Emotion_sentiment:Year_groups,data=emotion_df)
summary(lm2)



lm3 <- lm(as.factor(Emotion_sentiment) ~ 1 + Gender,data=emotion_df)
summary(lm3)
```
```{r}
install.packages("caret")
install.packages("gower")
install.packages("lifecycle", dependencies = TRUE)
update.packages(ask = FALSE, checkBuilt = TRUE)
library(gower)
library(caret)

y1989 <- subset(groupyear_combined, Year_groups == "1989-1993")
y1994 <- subset(groupyear_combined, Year_groups == "1994-1997")
y1998 <- subset(groupyear_combined, Year_groups == "1998-2001")
y2002 <- subset(groupyear_combined, Year_groups == "2002-2005")
y2006 <- subset(groupyear_combined, Year_groups == "2006-2009")
y2010 <- subset(groupyear_combined, Year_groups == "2010-2013")
y2014 <- subset(groupyear_combined, Year_groups == "2014-2017")

df_list <- list(y1989, y1994, y1998, y2002, y2006, y2010, y2014)

# Loop through the dataframes and downsample one class to match the size of the other class
for (i in df_list) {
  min_class <- names(which.min(table(i$Gender_label)))
  df_downsampled <- downsample(i[i$Gender_label == min_class, ], i[i$Gender_label != min_class, ])
}

#Shuffle the data before creating test-sets
shuf_y1989 <- y1989[sample(nrow(y1989)), ]
shuf_y1994 <- y1994[sample(nrow(y1994)), ]
shuf_y1998 <- y1998[sample(nrow(y1998)), ]
shuf_y2002 <- y2002[sample(nrow(y2002)), ]
shuf_y2006 <- y2006[sample(nrow(y2006)), ]
shuf_y2010 <- y2010[sample(nrow(y2010)), ]
shuf_y2014 <- y2014[sample(nrow(y2014)), ]

# Split the data into 3 folds
folds <- createDataPartition(df$target, p = 0.8, list = TRUE, times = 3)

# Use the folds to create the three dataframes
train <- df[folds[[1]], ]
validation <- df[folds[[2]], ]
test <- df[folds[[3]], ]


```

